### 2019-09-16 papers/journal/problem.tex
Connectivity is handled

The $k$-connectedness property is computationally challenging as it requires reasoning about all possible $k - 1$ edge removals. 
%
So instead of checking for the graph to be $k$-connected, the encoding and the implementation checks whether the graph is not $k+1$-connected.
%
Note that this check is sufficient as we are starting from smallest $k$ ($k = 1$) and subsequently incrementing it by one.     
% Used E as edge and L_e L_n as label for node and the edge,

@@

\subsection{Search for universal condition}
%
% Similarly, for the conjecture that k-connectedness is a universal condition for the VTS,
For some $k>0$,
we have to ensure that every graph of $k$-connected structure satisfies all
the rules of the system.
%
We also aim to find the minimum $k$. 
% We also have to ensure that the particular k is the least one. 
%
This condition can be specified as: for every $k$-connected graph, there exists a satisfiable assignment following the rules of the system. 
%
% \begin{align*}
%   & \forall G \, \texttt{Connectivity(k)} \implies  \exists
%                         f,p: \texttt{Stability} \, \land \, \texttt{Fusion}  
%   \tag{U}\label{eq:univcond}
% \end{align*}
%
We will use the same procedure as the existential condition to ensure that $k$ is minimized.
%
The formula for the problem has quantifier alternation. 
%
Most SAT solvers can check (at least efficiently) only quantifier-free formulas.
%
We need a QBF solver for such queries.
%

>>>>

The specification of the $k$-connectedness property is challenging as it requires reasoning about all possible $k - 1$ edge removals. 
%
So instead of checking for the graph to be $k$-connected, the encoding (and the implementation) checks whether the graph is not $k+1$-connected.
%
Note that this check is sufficient as we are starting from smallest $k$ ($k = 1$) and subsequently incrementing it by one.     
% Used E as edge and L_e L_n as label for node and the edge,

@@

\subsection{Search for universal condition}
%
% Similarly, for the conjecture that k-connectedness is a universal condition for the VTS,
For some $k>0$,
we have to ensure that every graph of $k$-connected structure satisfies all
the rules of the system.
%
We also aim to find the minimum $k$. 
% We also have to ensure that the particular k is the least one. 
%
This condition can be specified as: for every $k$-connected graph, there exists a satisfiable assignment following the rules of the system. 
%
% \begin{align*}
%   & \forall G \, \texttt{Connectivity(k)} \implies  \exists
%                         f,p: \texttt{Stability} \, \land \, \texttt{Fusion}  
%   \tag{U}\label{eq:univcond}
% \end{align*}
%
We will use the same procedure as the existential condition to ensure that $k$ is minimized.
%

%In the implementation, to conclude that a given $k$-connectedness is not a universal condition it is suffice to search for a $k$-connected graph that has no satisfying assignment of all the rules of the system, i.e., checking the negation of the condition is unsatisfiable.
%In the implementation, to conclude that a given $k$-connectedness is not a universal condition we search for a $k$-connected graph that has no satisfying assignment of all the rules of the system, i.e., checking the negation of the condition is unsatisfiable.
%
In the implementation instead of checking the satisfiability of the formula, we check whether the negation of the formula is unsatisfiable. That is to conclude that a given $k$-connectedness is not a universal condition we search for a $k$-connected graph that has no satisfying assignment of all the rules of the system.

The formula for the problem has quantifier alternation. 
%
Most SAT solvers can check (at least efficiently) only quantifier-free formulas.
%
%
We need a QBF solver for such queries. 
%
We refer the corresponding search problem as $\fqbf$ search problem.
%
